MinCall --- MinION od raw signala do genoma

### 2017-05-05 paper/main.tex
Added space after colon.

In this paper, we introduce the base caller for the MinION nanopore sequencing platform~\cite{mikheyev2014first}.The MinION device by Oxford Nanopore, weighing only 90 grams, is currently the smallest high-throughput DNA sequencer. Thanks to its low capital costs, small size and the possibility of analyzing the data in real time as they are produced, MinION is very promising for clinical applications, such as monitoring infectious disease outbreaks~\cite{judge2015early}\cite{quick2016real}, characterizing structural variants in cancer\cite{norris2016nanopore} and even full human genome assembly~\cite{jain2017nanopore}.

>>>>

In this paper, we introduce the base caller for the MinION nanopore sequencing platform~\cite{mikheyev2014first}. The MinION device by Oxford Nanopore, weighing only 90 grams, is currently the smallest high-throughput DNA sequencer. Thanks to its low capital costs, small size and the possibility of analyzing the data in real time as they are produced, MinION is very promising for clinical applications, such as monitoring infectious disease outbreaks~\cite{judge2015early}\cite{quick2016real}, characterizing structural variants in cancer\cite{norris2016nanopore} and even full human genome assembly~\cite{jain2017nanopore}.
